Homework Assignment 1 \\ Perceptron and Logistic Regression

### 2017-02-13 homeworks/hw1.tex
Compile hw1

\paragraph{2.} We used the following distance function for perceptron in the
lecture:
\begin{align*}
    D(M^*(\vx), M, \vx) = -\left( M^*(\vx) - M(\vx)
    \right) \left(\vw^\top
    \tilde{\vx}\right).
\end{align*}
This distance function has a problem of a trivial solution. What is the trivial
solution? Propose a solution to this.

>>>>

\paragraph{2.} We used the following distance function for perceptron in the
lecture:
\begin{align*}
    D(M^*(\vx), M, \vx) = -\left( M^*(\vx) - M(\vx)
    \right) \left(\vw^\top
    \tilde{\vx}\right).
\end{align*}
This distance function has a problem of a trivial solution. What is the trivial
solution? Propose a solution to this.
\\
\\
SOLUTION: The trivial solution is when we do not want to assign different weights to the input vector. As an example, if W is 0, then that means the distance function will always output 0, even if it shouldn't. To solve this, we need to somehow augment the weight vector to account for this situation and add a sort of intercept.
